### 2020-07-04 model.tex
final edits for 2nd draft

Moltres is an application built in the \gls{MOOSE} parallel finite element
framework \cite{lindsay_introduction_2018}. Similar to the physics modules in
\gls{MOOSE}, Moltres contains the necessary kernels representing various
physics and boundary conditions for solving for the neutron flux, delayed
neutron precursor concentration, and temperature. Together with the
Navier-Stokes module, it solves
the deterministic multigroup neutron diffusion and thermal-hydraulics
\glspl{PDE} simultaneously on the same mesh. Moltres supports up to 3-D meshes
and scales well for a large number of processors. The underlying \gls{MOOSE}
framework provides a range of implicit and explicit methods for the coupling
between the neutronics and thermal-hydraulics governing equations.

@@

The neutron flux calculations in the central core region are
performed using the standard formulations for the time-dependent multigroup
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations \ref{eq:neut} and \ref{eq:dnp}:
%
\begin{align}
    \frac{1}{v_g} \frac{\partial \phi_g}{\partial t} &= \nabla \cdot D_g
    \nabla \phi_g - \Sigma^r_g \phi_g +
    \sum^G_{g' \neq g} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
    \sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
    \lambda_i C_i, \label{eq:neut} \\
    \frac{\partial C_i}{\partial t} &= \beta_i \sum^G_{g'=1} \nu \Sigma^f_{g'}
    \phi_{g'} - \lambda_i C_i - \boldsymbol{u} \cdot \nabla C_i + \nabla \cdot
    K \nabla C_i, \label{eq:dnp} \\
    \intertext{where}
    v_g &= \text{average speed of neutrons in group $g$ [cm$\cdot$s$^{-1}$],} 
    \nonumber \\
    \phi_g &= \text{neutron flux in group $g$ [cm$^{-2}\cdot$s$^{-1}$],}
    \nonumber \\
    t &= \text{time [s],} \nonumber \\
    D_g &= \text{diffusion coefficient of neutrons in group $g$
    [cm$^2\cdot$s$^{-1}$],} \nonumber \\
    \Sigma^r_g &= \text{macroscopic cross section for removal of neutrons from
    group $g$ [cm$^{-1}$],} \nonumber \\
    \Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross section of
    scattering from $g'$ to $g$ [cm$^{-1}$],} \nonumber \\
    \chi^p_g &= \text{prompt fission spectrum for neutrons in group $g$,}
    \nonumber \\
    G &= \text{total number of discrete neutron groups,} \nonumber \\
    \nu &= \text{average number of neutrons produced per fission,} \nonumber
    \\
    \Sigma^f_{g} &= \text{macroscopic fission cross section for neutron in
    group $g$ [cm$^{-1}$],} \nonumber \\
    \chi^d_g &= \text{delayed fission spectrum for neutrons in group $g$,}
    \nonumber \\
    I &= \text{total number of delayed neutron precursor groups,} \nonumber \\
    \beta &= \text{total delayed neutron fraction,} \nonumber \\
    \beta_i &= \text{delayed neutron fraction of precursor group $i$,}
    \nonumber \\
    \lambda_i &= \text{average decay constant of delayed neutron precursors in
    precursor group $i$ [s$^{-1}$],} \nonumber \\
    C_i &= \text{concentration of delayed neutron precursors in precursor
    group $i$ [cm$^{-3}$],} \nonumber \\
    K &= \text{turbulent diffusion of the delayed neutron precursors
    [cm$^2\cdot$s$^{-1}$].} \nonumber
\end{align}
%

@@

\begin{figure}[htb!]
    \centering
    \includegraphics[width=.8\textwidth]{mesh}
    \caption{Mesh adopted in Moltres and a close-up view of the mesh around
    the boron carbide absorber.}
    \label{fig:mesh}
\end{figure}

@@

The \gls{MSFR} model in this work six neutron energy groups according to the
energy boundaries in table \ref{table:bound}, and eight \gls{DNP} groups as
defined by the JEFF-3.1.2 library. The neutron flux
and \gls{DNP} concentration values were approximated by first-order Lagrange
and constant monomial shape functions respectively on the finite element mesh.
Figure \ref{fig:mesh} shows the mesh adopted for the \gls{MSFR} model.
We assumed vacuum boundary conditions for all six neutron group fluxes along
the external boundaries of the geometry, and homogeneous Neumann boundary
conditions along the axial symmetry boundary. For the \gls{DNP}
concentrations, we imposed homogeneous Neumann boundary conditions on the
walls, and inflow and outflow boundary conditions on the inlet and outlet
boundaries respectively. The inlet \gls{DNP} concentration values were
imported from the outlet values of the 1-D outer loop pipe at the same
timestep.

For the decay heat model, a previous study on the MSFR by Aufiero et al.
\cite{aufiero_extended_2013} showed that using three decay heat precursor
groups with appropriate half-lives in the form of exponential equations, can
accurately model decay heat in the MSFR for up to 300 seconds after shutdown
with a relative error of less than 2\%. Thus, this thesis implements the new
decay heat modeling capability with the following equation:
%
\begin{align}
	\frac{\partial \omega_j}{\partial t} &= f_j \sum^G_{g=1} \epsilon_{g}
	\Sigma^f_{g} \phi_{g} - \lambda_j \omega_j - \boldsymbol{u} \cdot \nabla
	\omega_j + \nabla \cdot K \nabla \omega_j, \label{eq:decayheat} \\
	\intertext{where}
    \omega_j &= \text{total decay heat power density from decay heat
    precursors in group $j$ [W$\cdot$cm$^{-3}$],} \nonumber \\
	f_j &= \text{fraction of decay heat from group $j$ to total power under
	full-power conditions,}
	\nonumber \\
	\epsilon_g &= \text{average fission energy per fission [W],} \nonumber \\
	\lambda_j &= \text{average decay constant of decay heat precursors in
	group $j$ [s$^{-1}$].} \nonumber
\end{align}

@@

This work models fluid dynamics using the \gls{INS} capabilities from the
MOOSE Navier-Stokes module \cite{peterson_overview_2017}. The standard
\gls{INS} equations are:
%
\begin{align}
    \text{Momentum eq.:} && \rho \frac{\partial \boldsymbol{u}}{\partial t} &=
    -\rho (\boldsymbol{u}
    \cdot \nabla) \boldsymbol{u} + \nabla \cdot (-p \boldsymbol{I} + \mu [
    \nabla \boldsymbol{u} + (\nabla \boldsymbol{u})^T] + \boldsymbol{f} &&
    \label{eq:momemtum} \\
    \text{Divergence-free:} && \nabla \cdot \boldsymbol{u} &= 0 &&
    \label{eq:divergence}
    \intertext{where}
    && p &= \text{ pressure [Pa],} && \nonumber \\
    && \mu &= \text{ dynamic viscosity [Pa s],} && \nonumber \\
    && \boldsymbol{f} &= \text{ body force per unit volume [N m$^{-3}$].} &&
    \nonumber
\end{align}

@@

The energy balance equation for temperature used in this Moltres model is:
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p \boldsymbol{u}
    \cdot \nabla T + \nabla \cdot [(k + k_t) \nabla T] + Q_s
    \label{eq:temp} \\
    k_t &= \frac{\mu_t}{\rho Pr_t} \\
    Q_s &= \Big( 1 - \sum^J_{j=1} f_j \Big) \sum^G_{g=1} \epsilon_g \Sigma_g^f
    \phi_g + \sum^J_{j=1} \omega_j, \label{eq:source}
    \intertext{where}
    c_p &= \text{specific heat capacity of molten salt
    [J$\cdot$kg$^{-1}\cdot$K$^{-1}$],} \nonumber \\
    T &= \text{temperature of molten salt [K]} \nonumber \\
    \boldsymbol{u} &= \text{velocity of molten salt [m$\cdot$s$^{-1}$],}
    \nonumber \\
    k &= \text{thermal conductivity of molten salt
    [W$\cdot$m$^{-1}\cdot$K$^{-1}$],} \nonumber \\
    J &= \text{total number of decay heat groups.} \nonumber
\end{align}
%
The diffusion term includes turbulent heat
diffusivity based on the eddy viscosity $\mu_t$ and the turbulent Prandtl
number $Pr_t$. $Pr_t$ is also 0.85 due to the same reasoning provided for
$Sc_t$. The first term in the heat source $Q_s$ equation represents prompt
fission heat, and the second term represents decay heat from the $J$ decay
heat groups.

We expected good qualitative agreement with the Polimi and TUDelft models,
including the large recirculation region near the blanket tank walls and the
resulting high temperatures in that region. There would be some minor
discrepancies where the viscosity values are under- or over-predicted, leading
to slightly inaccurate temperature and precursor concentration values from
turbulent diffusion.

@@

Since this region is largely subcritical, the only significant
neutronics-related phenomena are the drift, and decay of \glspl{DNP}.
The governing equation for the \glspl{DNP} is:
%
\begin{align}
    \frac{\partial C_i}{\partial t} &= - \lambda_i C_i - u
    \frac{\partial C_i}{\partial x} + D_t \frac{\partial^2 C_i}{\partial x^2}.
    \label{eq:dnploop}
\end{align}
%
Equation \ref{eq:dnploop} is derived from equation \ref{eq:dnp} by removing
the fission \gls{DNP} source term, and the conversion of the advection and
diffusion terms to their 1-D forms. The decay constants and diffusion
coefficient are the same values used in the central core region.

@@

Instead of the Navier-Stokes equations, we have a predetermined velocity of
1.1275 m s$^{-1}$ in the outer loop region. The governing equation for
temperature, derived from equation \ref{eq:temp}, is:
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p u
    \frac{\partial T}{\partial x} - Q_{hx} \label{eq:temploop} \\
    Q_{hx} &= \alpha (T - T_i) \delta (x_0) \label{eq:hx} \\
    \intertext{where}
    \alpha &= \text{heat transfer coefficient [W K$^{-1}$],} \nonumber \\
    x_0 &= \text{position of the point heat exchanger [m].} \nonumber
\end{align}

The fission heat source term is replaced with a heat exchanger sink term
which depends on the temperature difference between the fuel salt $T$ and the
secondary loop salt $T_s$. For simplicity, we assumed a constant temperature
of 823 K in the secondary loop. The heat transfer coefficient was determined
by assuming that the fuel outlet temperature is 1023 K and calculating the
heat removal rate to induce a 100 K drop at the given volumetric flow rate
and heat capacity of the fuel salt. We opted to ignore the diffusion term due
to the discontinuity of the temperature distribution across the point heat
exchanger.

\subsection{Boundary Conditions and Flow Transfers}

This subsection details the various boundary conditions for all of the
tracked variables, and the \gls{DNP} and temperature flow transfers between
the central core and outer loop regions.

Starting with the central core region, for the neutron group fluxes, we
imposed vacuum boundary conditions on the
outermost boundaries of the geometry in Figure \ref{fig:core} excluding the
axial boundary. The \gls{DNP} variables have homogeneous Neumann boundary
conditions along the axis and the walls in the central core region, and inflow
and outflow boundary conditions on the inlet and outlet boundaries,
respectively. The temperature variable shares the same type of boundary
conditions as the \gls{DNP} variables.

The flow rate is dictated by an inflow boundary condition at the core inlet
for a volumetric flow rate of 4.5 m$^3$ s$^{-1}$. We imposed no-slip boundary
conditions on the walls of the central core, and homogeneous Neumann boundary
conditions on the outlet. Along the axial boundary, we have homogeneous
Dirichlet boundary condition for the radial velocity component, and
homogeneous Neumann boundary condition for the axial velocity component.

At every timestep, Moltres also calculates weighted averages of the
temperature and \gls{DNP} at the outlet. These values are weighted by the
outflow velocity values at the outlet according to the following equation:
%
\begin{align}
    \overline{\phi} &= \frac{\int_\mathcal{C} \phi(y) u(y) dy}{
    \int_\mathcal{C} u(y) dy} \\
    \intertext{where}
    \phi &= \text{variable to be weighted} \nonumber \\
    \mathcal{C} &= \text{outlet boundary curve} \nonumber \\
    u &= \text{outflow velocity perpendicular to the outlet boundary [m
    s$^{-1}$].} \nonumber
\end{align}

>>>>

Moltres is an application built in the \gls{MOOSE} parallel finite element
framework \cite{lindsay_introduction_2018}. Similar to the physics modules in
\gls{MOOSE}, Moltres contains the necessary kernels representing various
physics and boundary conditions for solving for the neutron flux, delayed
neutron precursor concentration, and temperature. Together with the
Navier-Stokes module, it solves
the deterministic multigroup neutron diffusion and thermal-hydraulics
\glspl{PDE} simultaneously on the same mesh. Moltres supports up to 3-D meshes
and scales well over a large number of processors. The underlying \gls{MOOSE}
framework provides a range of implicit and explicit methods for the coupling
between the neutronics and thermal-hydraulics governing equations.

@@

The neutron flux calculations in the central core region are
performed using the standard formulations for the time-dependent multigroup
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations \ref{eq:neut} and \ref{eq:dnp}:
%
\begin{align}
    \frac{1}{v_g} \frac{\partial \phi_g}{\partial t} &= \nabla \cdot D_g
    \nabla \phi_g - \Sigma^r_g \phi_g +
    \sum^G_{g' \neq g} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
    \sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
    \lambda_i C_i, \label{eq:neut} \\
    \frac{\partial C_i}{\partial t} &= \beta_i \sum^G_{g'=1} \nu \Sigma^f_{g'}
    \phi_{g'} - \lambda_i C_i - \vec{u} \cdot \nabla C_i + \nabla \cdot
    K \nabla C_i, \label{eq:dnp} \\
    \intertext{where}
    v_g &= \text{average speed of neutrons in group $g$ [cm$\cdot$s$^{-1}$],} 
    \nonumber \\
    \phi_g &= \text{neutron flux in group $g$ [cm$^{-2}\cdot$s$^{-1}$],}
    \nonumber \\
    t &= \text{time [s],} \nonumber \\
    D_g &= \text{diffusion coefficient of neutrons in group $g$
    [cm$^2\cdot$s$^{-1}$],} \nonumber \\
    \Sigma^r_g &= \text{macroscopic cross section for removal of neutrons from
    group $g$ [cm$^{-1}$],} \nonumber \\
    \Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross section of
    scattering from $g'$ to $g$ [cm$^{-1}$],} \nonumber \\
    \chi^p_g &= \text{prompt fission spectrum for neutrons in group $g$,}
    \nonumber \\
    G &= \text{total number of discrete neutron groups,} \nonumber \\
    \nu &= \text{average number of neutrons produced per fission,} \nonumber
    \\
    \Sigma^f_{g} &= \text{macroscopic fission cross section for neutron in
    group $g$ [cm$^{-1}$],} \nonumber \\
    \chi^d_g &= \text{delayed fission spectrum for neutrons in group $g$,}
    \nonumber \\
    I &= \text{total number of delayed neutron precursor groups,} \nonumber \\
    \beta &= \text{total delayed neutron fraction,} \nonumber \\
    \beta_i &= \text{delayed neutron fraction of precursor group $i$,}
    \nonumber \\
    \lambda_i &= \text{average decay constant of delayed neutron precursors in
    precursor group $i$ [s$^{-1}$],} \nonumber \\
    C_i &= \text{concentration of delayed neutron precursors in precursor
    group $i$ [cm$^{-3}$],} \nonumber \\
    K &= \text{turbulent diffusion of the delayed neutron precursors
    [cm$^2\cdot$s$^{-1}$].} \nonumber
\end{align}
%

@@

\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{mesh2}
    \caption{Mesh adopted in Moltres and a close-up view of the mesh around
    the boron carbide absorber.}
    \label{fig:mesh}
\end{figure}

@@

The \gls{MSFR} model in this work six neutron energy groups according to the
energy boundaries in table \ref{table:bound}, and eight \gls{DNP} groups as
defined by the JEFF-3.1.2 library. The neutron flux
and \gls{DNP} concentration values were approximated by first-order Lagrange
and constant monomial shape functions respectively on the finite element mesh.
Figure \ref{fig:mesh} shows the mesh adopted for the \gls{MSFR} model.
This work assumes vacuum boundary conditions for all six neutron group fluxes
along
the external boundaries of the geometry, and homogeneous Neumann boundary
conditions along the axial symmetry boundary. For the \gls{DNP}
concentrations, we imposed homogeneous Neumann boundary conditions on the
walls, and inflow and outflow boundary conditions on the inlet and outlet
boundaries respectively. The inlet \gls{DNP} concentration values were
imported from the outlet values of the 1-D outer loop pipe at the same
timestep.

For the decay heat model, a previous study on the MSFR by Aufiero et al.
\cite{aufiero_extended_2013} showed that using three decay heat precursor
groups with appropriate half-lives in the form of exponential equations, can
accurately model decay heat in the MSFR for up to 300 seconds after shutdown
with a relative error of less than 2\%. Thus, this thesis implements the new
decay heat modeling capability with the following equation:
%
\begin{align}
	\frac{\partial \omega_j}{\partial t} &= f_j \sum^G_{g=1} \epsilon_{g}
	\Sigma^f_{g} \phi_{g} - \lambda_j \omega_j - \vec{u} \cdot \nabla
	\omega_j + \nabla \cdot K \nabla \omega_j, \label{eq:decayheat} \\
	\intertext{where}
    \omega_j &= \text{total decay heat power density from decay heat
    precursors in group $j$ [W$\cdot$cm$^{-3}$],} \nonumber \\
	f_j &= \text{fraction of decay heat from group $j$ to total power under
	full-power conditions,}
	\nonumber \\
	\epsilon_g &= \text{average fission energy per fission [W],} \nonumber \\
	\lambda_j &= \text{average decay constant of decay heat precursors in
	group $j$ [s$^{-1}$].} \nonumber
\end{align}

@@

This work models fluid dynamics using the \gls{INS} capabilities from the
MOOSE Navier-Stokes module \cite{peterson_overview_2017}. The standard
\gls{INS} equations are:
%
\begin{align}
    \text{Momentum eq.:} && \rho \frac{\partial \vec{u}}{\partial t} &=
    -\rho (\vec{u}
    \cdot \nabla) \vec{u} + \nabla \cdot (-p \vec{I} + \mu [
    \nabla \vec{u} + (\nabla \vec{u})^T] + \vec{f} &&
    \label{eq:momemtum} \\
    \text{Divergence-free:} && \nabla \cdot \vec{u} &= 0 &&
    \label{eq:divergence}
    \intertext{where}
    && p &= \text{ pressure [Pa],} && \nonumber \\
    && \mu &= \text{ dynamic viscosity [Pa s],} && \nonumber \\
    && \vec{f} &= \text{ body force per unit volume [N$\cdot$m$^{-3}$].} &&
    \nonumber
\end{align}

@@

The energy balance equation for temperature used in this Moltres model is:
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p \vec{u}
    \cdot \nabla T + \nabla \cdot [(k + k_t) \nabla T] + Q_s
    \label{eq:temp} \\
    k_t &= \frac{\mu_t}{\rho Pr_t} \\
    Q_s &= \Big( 1 - \sum^J_{j=1} f_j \Big) \sum^G_{g=1} \epsilon_g \Sigma_g^f
    \phi_g + \sum^J_{j=1} \omega_j, \label{eq:source}
    \intertext{where}
    c_p &= \text{specific heat capacity of molten salt
    [J$\cdot$kg$^{-1}\cdot$K$^{-1}$],} \nonumber \\
    T &= \text{temperature of molten salt [K]} \nonumber \\
    \vec{u} &= \text{velocity of molten salt [m$\cdot$s$^{-1}$],}
    \nonumber \\
    k &= \text{thermal conductivity of molten salt
    [W$\cdot$m$^{-1}\cdot$K$^{-1}$],} \nonumber \\
    J &= \text{total number of decay heat groups.} \nonumber
\end{align}
%
The diffusion term includes turbulent heat
diffusivity based on the eddy viscosity $\mu_t$ and the turbulent Prandtl
number $Pr_t$. $Pr_t$ is also 0.85 due to the same reasoning provided for
$Sc_t$. The first term in the heat source $Q_s$ equation represents prompt
fission heat, and the second term represents decay heat from the $J$ decay
heat groups.

With this model, the results were expected to show good qualitative agreement
with the Polimi and TUDelft models, including the large recirculation region
near the blanket tank walls and the resulting high temperatures in that
region. The results in Chapter \ref{chap:ss} would be some minor
discrepancies where the viscosity values are under- or over-predicted, leading
to minor inaccuracies in temperature and precursor concentration distributions
from turbulent diffusion.

\subsubsection{Boundary Conditions}

Table \ref{table:corebc} summarizes the boundary conditions for all variables
on all of the relevant boundaries. Figure \ref{fig:msfrbc} shows the locations
of the various boundaries listed in the table.

\begin{table}[htbp!]
    \small
	\caption{Boundary conditions in the main reactor geometry (Figure
	\ref{fig:msfrbc}.}
	\centering
	\begin{tabular}{ l l c}
		\toprule
		Variable & Boundary & Boundary Condition \\
		\midrule
		\multirow{4}{*}{Neutron flux $\phi_g$} & Top & $\frac{d \phi_g}{dx}
		\big|_{\text{inflow}} = 0$ \\
        & Outer & $\frac{d \phi_g}{dx} \big|_{\text{inflow}} = 0$ \\
        & Bottom & $\frac{d \phi_g}{dx} \big|_{\text{inflow}} = 0$ \\
        & Axial & $\frac{d \phi_g}{dx} = 0$ \\
        \midrule
        \multirow{6}{*}{Delayed neutron precursor concentration $C_i$} &
        Top (Core) & $\frac{d C_i}{dx} = 0$ \\
        & Bottom (Core) & $\frac{d C_i}{dx} = 0$ \\
        & Outer (Core) & $\frac{d C_i}{dx} = 0$ \\
        & Axial (Core) & $\frac{d C_i}{dx} = 0$ \\
        & Inlet (Core) & $C_i = c$ \\
        & Outlet (Core) & $u_x \cdot C_i = 0$ \\
        \midrule
        \multirow{6}{*}{Decay heat power density $\omega_j$} &
        Top (Core) & $\frac{d \omega_j}{dx} = 0$ \\
        & Bottom (Core) & $\frac{d \omega_j}{dx} = 0$ \\
        & Outer (Core) & $\frac{d \omega_j}{dx} = 0$ \\
        & Axial (Core) & $\frac{d \omega_j}{dx} = 0$ \\
        & Inlet (Core) & $\omega_j = c$ \\
        & Outlet (Core) & $u_x \cdot \omega_j = 0$ \\
        \midrule
        \multirow{6}{*}{Radial velocity $u_x$} & Top (Core) & $u_x = 0$ \\
        & Bottom (Core) & $u_x = 0$ \\
        & Outer (Core) & $u_x = 0$ \\
        & Axial (Core) & $u_x = 0$ \\
        & Inlet (Core) & $u_x = c$ \\
        & Outlet (Core) & $\frac{d u_x}{dx} = 0$ \\
        \midrule
        \multirow{6}{*}{Axial velocity $u_y$} & Top (Core) & $u_y = 0$ \\
        & Bottom (Core) & $u_y = 0$ \\
        & Outer (Core) & $u_y = 0$ \\
        & Axial (Core) & $\frac{d u_y}{dx} = 0$ \\
        & Inlet (Core) & $u_y = 0$ \\
        & Outlet (Core) & $\frac{d u_y}{dx} = 0$ \\
        \midrule
        \multirow{6}{*}{Temperature $T$} & Top (Core) &
        $\frac{d T}{dx} = 0$ \\
        & Bottom (Core) & $\frac{d T}{dx} = 0$ \\
        & Outer (Core) & $\frac{d T}{dx} = 0$ \\
        & Axial (Core) & $\frac{d T}{dx} = 0$ \\
        & Inlet (Core) & $T = c$ \\
        & Outlet (Core) & $\frac{d T}{dx} = 0$ \\
		\bottomrule
	\end{tabular}
	\label{table:corebc}
\end{table}

\clearpage

\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{msfrbc}
    \caption{The boundaries in the \gls{MSFR} geometry that are relevant for
    the boundary conditions mentioned in Table \ref{table:corebc}.}
    \label{fig:msfrbc}
\end{figure}

@@

Since this outer loop region is largely subcritical, the only significant
neutronics-related phenomena are the drift and decay of \glspl{DNP}.
The governing equation for the \glspl{DNP} is:
%
\begin{align}
    \frac{\partial C_i}{\partial t} &= - \lambda_i C_i - u
    \frac{\partial C_i}{\partial x}.
    \label{eq:dnploop}
\end{align}
%
Equation \ref{eq:dnploop} is derived from equation \ref{eq:dnp} by removing
the fission \gls{DNP} source term, and the conversion of the advection and
diffusion terms to their 1-D forms. The decay constants and diffusion
coefficient are the same values used in the central core region.

@@

A constant velocity of 1.1275 m s$^{-1}$ is applied in the outer loop region.
The governing equation for
temperature, derived from equation \ref{eq:temp}, is:
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p u
    \frac{\partial T}{\partial x} - Q_{hx} \label{eq:temploop} \\
    Q_{hx} &= \alpha (T - T_i) \delta (x_0) \label{eq:hx} \\
    \intertext{where}
    Q_{hx} &= \text{heat removal rate through the heat exchanger [W],} 
    \nonumber \\
    \alpha &= \text{heat transfer coefficient [W$\cdot$K$^{-1}$],} \nonumber
    \\
    T_i &= \text{temperature of the intermediate salt [K],} \nonumber \\
    x_0 &= \text{position of the point heat exchanger [m].} \nonumber
\end{align}

The fission heat source term is replaced with a heat exchanger sink term
$Q_{hx}$
which depends on the temperature difference between the fuel salt $T$ and the
intermediate loop salt $T_i$. For simplicity, this work assumes a constant
temperature of 823 K in the intermediate loop. The heat transfer coefficient
was determined by assuming that the fuel outlet temperature is 1023 K and
calculating the heat removal rate to induce a 100 K drop at the given
volumetric flow rate and heat capacity of the fuel salt. The resulting value
for $\alpha$ is 370.668 W$\cdot$K$^{-1}$. This work opted to
ignore the diffusion term due to the discontinuity of the temperature
distribution across the point heat exchanger.

\subsubsection{Boundary Conditions}

Table \ref{table:loopbc} summarizes the boundary conditions for all variables
on the inlet and outlet of the 1-D outer loop region.

\begin{table}[htbp!]
    \small
	\caption{Boundary conditions in the 1-D outer loop geometry. $u$
	represents the 1-D velocity in this region.}
	\centering
	\begin{tabular}{ l l c}
		\toprule
		Variable & Boundary & Boundary Condition \\
        \midrule
        \multirow{2}{*}{Delayed neutron precursor concentration $C_i$} &
        Inlet (Core) & $C_i = c$ \\
        & Outlet (Core) & $u \cdot C_i = 0$ \\
        \midrule
        \multirow{2}{*}{Decay heat power density $\omega_j$} &
        Inlet (Core) & $\omega_j = c$ \\
        & Outlet (Core) & $u \cdot \omega_j = 0$ \\
        \midrule
        \multirow{2}{*}{Temperature $T$} &
        Inlet (Core) & $T = c$ \\
        & Outlet (Core) & $u \cdot T = 0$ \\
		\bottomrule
	\end{tabular}
	\label{table:loopbc}
\end{table}

\subsection{Flow Transfers}

This subsection details the delayed neutron and decay heat precursors, and
temperature flow transfers between the central core and outer loop regions.

%Starting with the central core region, for the neutron group fluxes, we
%imposed vacuum boundary conditions on the
%outermost boundaries of the geometry in Figure \ref{fig:core} excluding the
%axial boundary. The \gls{DNP} variables have homogeneous Neumann boundary
%conditions along the axis and the walls in the central core region, and inflow
%and outflow boundary conditions on the inlet and outlet boundaries,
%respectively. The temperature variable shares the same type of boundary
%conditions as the \gls{DNP} variables.

A parabolic flow profile was imposed on the inlet Dirichlet boundary
condition. The equation for $u_x$ at the inlet is:
%
\begin{align}
    u_x &= -2034.01 \Big[\frac{y}{18.75} - \Big(\frac{y}{18.75}\Big)^2 
    \Big] \\
    \intertext{where}
    y = \text{height along the inlet [cm].}
\end{align}
%
The inlet is 18.75 cm high, and the coefficient at the front is from
normalizing the equation for a total volumetric flow rate of
4.5 m$^3$ s$^{-1}$.

At every timestep, Moltres also calculates weighted averages of the
temperature and the precursors at the outlet. These values are weighted by the
outflow velocity values at the outlet according to the following equation:
%
\begin{align}
    \overline{\psi} &= \frac{\int_\mathcal{C} \psi(y) u(y) dy}{
    \int_\mathcal{C} u(y) dy} \\
    \intertext{where}
    \psi &= \text{variable to be weighted} \nonumber \\
    \mathcal{C} &= \text{outlet boundary curve} \nonumber \\
    u &= \text{outflow velocity perpendicular to the outlet boundary [m
    s$^{-1}$].} \nonumber
\end{align}
